\section{Expressiveness of \toolname}\label{sec:express}
To understand the expressiveness of our tool, we encoded the common vulnerabilities in 
smart contracts described in prior work~\cite{attack-time,smart-sec} and on social 
media~\cite{batch-news}. 
In particular, Table~\ref{tbl:expr} summarizes the expressiveness of mainstream tools
for smart contract security, ordered by publish date. Note that our tool  
 supports not only well-known vulnerabilities such as Reentrancy, Timestamp Dependency,
 and Arithmetic operations (i.e., over/underflow), but also recent attacks
 such as the \batchoverflow vulnerability discussed 
 in Section~\ref{sec:overview}. Prior tools express 
 a portion of these vulnerabilities. For instance, the \oyente~\cite{oyente} 
 tool, which is also based on symbolic execution, does not support vulnerabilities such as 
 unchecked calls and out-of-gas-DoS. Static analysis tools such as 
 Securify~\cite{securify} and \madmax~\cite{madmax} do not support complex arithmetic vulnerabilities.
Most importantly, unlike \toolname, 
 none of them can generate exploits for vulnerabilities. The \teether and the 
 \contractfuzz tools can automatically generate 
 exploits, but their systems only support a small class of vulnerabilities.

 There are some vulnerabilities that our tool does not support well. 
 For instance, a Transaction-Ordering Dependency (TOD) is a race condition 
 vulnerability, and exploiting it requires synthesizing \emph{a pair of programs}
 that exhibit the race. In the future, we plan to explore \emph{relational synthesis}
 to handle attacks that require multiple programs. Another source of limitation
 is denial-of-service (DoS) attacks that involve loops, which our tool unrolls during 
 symbolic execution, and the unrolling bound may not be large enough to
 trigger the vulnerability.


\begin{table*}[]
\centering
\scriptsize
\begin{tabular}{|l|c|c|c|c|c|c|c|c|c|}
\hline
\multicolumn{1}{|c|}{\multirow{2}{*}{Tool}} & \multicolumn{1}{l|}{\multirow{2}{*}{\begin{tabular}[c]{@{}l@{}}Generate\\ Exploit?\end{tabular}}} & \multicolumn{8}{c|}{Common Vulnerabilities}        \\ \cline{3-10} 
\multicolumn{1}{|c|}{}                      & \multicolumn{1}{l|}{}                                                                             & \multicolumn{1}{l|}{Reentrance} & \multicolumn{1}{l|}{Arithmetic} & \multicolumn{1}{l|}{DoS} & \multicolumn{1}{l|}{\begin{tabular}[c]{@{}l@{}}Bad \\ Random\end{tabular}} & \multicolumn{1}{l|}{Timestamp} & \multicolumn{1}{l|}{TOD} & \multicolumn{1}{l|}{\begin{tabular}[c]{@{}l@{}}Unchecked \\ Calls\end{tabular}} & \multicolumn{1}{l|}{\begin{tabular}[c]{@{}l@{}}Attack \\ Control\end{tabular}}  \\ \hline
\oyente    & \LEFTcircle      & \cmark       &\cmark         &               &         & \cmark     & \LEFTcircle       &               &                           \\ \hline
Mythril    &  \LEFTcircle     & \cmark       & \cmark        &               &         & \cmark     & \LEFTcircle       & \cmark        & \cmark                    \\ \hline
Zeus       &                  & \cmark       & \cmark        &               &         & \cmark     & \LEFTcircle       & \cmark        & \cmark                     \\ \hline
\teether    & \cmark           &              &               &               &         &            &                   &               & \cmark                     \\ \hline
Securify   &                  & \cmark       &               &               &         & \cmark     & \LEFTcircle       & \cmark        & \cmark                     \\ \hline
\madmax    &                  &              & \LEFTcircle   & \LEFTcircle   &         &            &                   &               &                            \\ \hline
\contractfuzz & \cmark       & \cmark       &               &               &\cmark   & \cmark     & \LEFTcircle       &               &                             \\ \hline
\toolname  & \cmark           & \cmark       & \cmark        & \LEFTcircle   & \cmark  & \cmark     & \LEFTcircle       & \cmark        & \cmark                      \\ \hline
\end{tabular}
\caption{A Comparison of Existing Tools (\oyente~\cite{oyente}, Mythril~\cite{mythril}, Zeus~\cite{zeus}, \teether~\cite{teether}, Securify~\cite{securify}, \madmax~\cite{madmax}, and ContractFuzzer~\cite{contractfuzzer}) for Smart Contract (Order by publish date). \LEFTcircle \ represents limited support.}. 
\label{tbl:expr}
\end{table*}
